I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-09 Paper/Paper_noProof.tex
image

\section{Background}

We follow some notions in PRIMA's and Beta-Crown's papers: we use lower case Latin for scalars, bold for vectors
$\boldsymbol{z}$, capitalized bold for matrices $\boldsymbol{W}$. In this paper, we will not use tensors with a dimension higher than matrices: those will be flattened.

@@

@@

>>>>

\section{Preliminaries}

In this paper, we will use lower case Latin $a$ for scalars, bold for vectors $\boldsymbol{z}$, 
capitalized bold for matrices $\boldsymbol{W}$, similar to 
notations in \cite{prima,crown}.

%In this paper, we will not use tensors with a dimension higher than matrices: those will be flattened.

@@

\begin{figure}[t!]
\centering
	\includegraphics[scale=0.4]{example.png}
\caption{A DNN example from \cite{kneuron}}
\label{fig1}
\end{figure}

@@

% test
